Operational adoption of new probabilistic point rainfall forecasts: the crucial role of user-centric training

### 2020-11-30 manuscript/main.tex
Updates from Overleaf

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness.png}}
\caption{Effectiveness (EFF) of probabilistic forecasts in decision-making based on the pre-existing users' understanding (UND) of ensemble-based forecasts. Diagram's x-axis represents UND levels: "low", "medium", "high". Diagram's y-axis represents EFF levels: "ineffective", "moderately effective", "very effective". The red line represents the optimal UND-EFF relationship. The dashed area represents not possible values for such relationship. The blue line represents qualitatively the current UND-EFF relationship for traditional probabilistic ensemble-based forecasts. The dashed fuchsia line represents the estimated UND-EFF relationship for ecPoint forecasts.}
\label{ProbFC_Knowledge_Effectiveness}
\end{figure}

@@

>>>>

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness_Estimate.png}}
\caption{Relationship between understanding (UND) ensemble-based probabilistic forecasts and the ability of use them effectively (EFF) in decision-making processes. Diagram's x-axis represents UND levels: "low", "medium", "high". Diagram's y-axis represents EFF levels: "ineffective", "moderately effective", "very effective". The black line represents optimal UND-EFF relationships, and the black dashed area represents impossible values for such relationship. Training on ensemble-based probabilistic forecasts has pushed their understanding from "low" to "medium" or "high" levels (green arrow on x-axis). Training on the communication of ensemble-based probabilistic forecasts has pushed their effectiveness in decision-making processes from "ineffective" to "moderately effective" or "very effective" (green arrow in the y-axis). Qualitatively, the blue line represents state-of-the-art UND-EFF relationship for traditional probabilistic ensemble-based forecasts. The dashed red line represents the estimated UND-EFF relationship for ecPoint forecasts, and the fuchsia area between the blue and red lines represents the estimated gap between UND-EFF of ecPoint forecasts compared to traditional probabilistic forecasts.}
\label{UND_EFF_estimated}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness_Observed.png}}
\caption{Like Fig.\ref{UND_EFF_estimated}, but it includes the results of the experiment with IMN and OMSZ. Such results show that the gap in the UND-EFF relationship between ecPoint and traditional ensemble-based forecasts is greater than it was estimated at the beginning of the experiment as centres with different ensemble-based forecasts understanding levels performed similarly.}
\label{UND_EFF_observed}
\end{figure}
